% ============================================================
% SafeHer Research Paper - IEEE Two-Column Format
% ============================================================
\documentclass[conference,twocolumn]{IEEEtran}

% ---- Packages ----
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}           % Times New Roman font
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{float}
\usepackage{enumitem}
\usepackage{balance}
\usepackage{url}
\usepackage{multirow}

% ---- Code listing style ----
\definecolor{codegreen}{rgb}{0,0.5,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.96,0.96,0.96}

\lstdefinestyle{mystyle}{
  backgroundcolor=\color{backcolour},
  commentstyle=\color{codegreen},
  keywordstyle=\color{blue},
  stringstyle=\color{codepurple},
  basicstyle=\ttfamily\scriptsize,
  breakatwhitespace=false,
  breaklines=true,
  captionpos=b,
  keepspaces=true,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=2,
  frame=single,
  framesep=2pt,
  xleftmargin=4pt,
  xrightmargin=4pt,
}
\lstset{style=mystyle}

% ---- Hyperref setup ----
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

% ============================================================
\begin{document}

% ---- Title ----
\title{SafeHer: A Proactive AI-Driven Safety System for Women Using Contextual Risk Assessment and Real-Time Monitoring}

\author{
  \IEEEauthorblockN{Rohit Kumar Yadav\IEEEauthorrefmark{1}, Aditya Upadhyay\IEEEauthorrefmark{2}, Kajal Kasaudhan\IEEEauthorrefmark{3}, and Dr. Nikhat Akhtar\IEEEauthorrefmark{4}}
  \IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}\IEEEauthorrefmark{3}UG student, Department of Computer Science and Engineering\\
  Goel Institute of Technology and Management, Lucknow, Uttar Pradesh, India}
  \IEEEauthorblockA{\IEEEauthorrefmark{4}Professor, Department of Computer Science and Engineering\\
  Goel Institute of Technology and Management, Lucknow, Uttar Pradesh, India}
}

\maketitle

% ---- Abstract ----
\begin{abstract}
Women's safety remains a critical global concern, particularly in urban and semi-urban environments where manual panic-button apps often fail during high-stress emergencies. This paper presents SafeHer, a proactive, AI-driven mobile safety system that shifts personal protection from reactive alerting to predictive risk assessment. The system continuously monitors contextual mobile sensor data---including GPS location, motion patterns, time-of-day, and environmental isolation---and processes it through a hybrid Danger Score Engine. This engine combines rule-based risk thresholds with Google Gemini's contextual AI analysis to generate a dynamic risk score (0--100). When the score exceeds a predefined threshold, the system autonomously triggers emergency alerts to trusted contacts via Firebase Cloud Messaging, shares real-time location, and logs incident context without requiring user interaction. Built on a Flutter frontend with a scalable Firebase backend, SafeHer emphasizes privacy-preserving architecture, battery-optimized background tracking, offline resilience, and automated cloud workflows. Preliminary evaluations demonstrate an average alert latency of under 2.1 seconds, battery consumption of 8--12\% over 8 hours of background monitoring, and a contextual accuracy rate of approximately 89\% across simulated threat scenarios.
\end{abstract}

\begin{IEEEkeywords}
Women Safety, Predictive Safety Systems, AI-Based Risk Detection, Mobile Context Sensing, Firebase Architecture, Google Gemini AI, Proactive Alerting, Real-Time Location Tracking
\end{IEEEkeywords}

% ---- Input section files ----
\input{sections/introduction}
\input{sections/literature}
\input{sections/problemstatement}
\input{sections/architecture}
\input{sections/methodology}
\input{sections/implementation}
\input{sections/results}
\input{sections/discussion}
\input{sections/limitations}
\input{sections/futurework}
\input{sections/conclusion}

% ---- References ----
\begin{thebibliography}{18}

\bibitem{who2018}
World Health Organization, \emph{Violence Against Women: Global Estimates 2018}, Geneva, Switzerland: WHO Press, 2018.

\bibitem{dhillon2021}
S.~K. Dhillon and R.~K. Singh, ``Analysis of women safety apps: Limitations of reactive emergency response systems,'' \emph{Int. J. Comput. Sci. Inf. Technol.}, vol.~12, no.~4, pp.~112--118, 2021.

\bibitem{uddin2022}
A.~B.~M.~S. Uddin \emph{et~al.}, ``Context-aware mobile safety systems: A survey of sensing, prediction, and alerting mechanisms,'' \emph{IEEE Access}, vol.~10, pp.~45123--45139, 2022.

\bibitem{flutter2024}
Google LLC, \emph{Flutter Documentation: Cross-Platform UI Toolkit}, 2024. [Online]. Available: \url{https://docs.flutter.dev}

\bibitem{firebase2024}
Firebase Team, \emph{Firebase Cloud Firestore \& Authentication Documentation}, Google, 2024. [Online]. Available: \url{https://firebase.google.com/docs}

\bibitem{gemini2025}
Google DeepMind, \emph{Google Gemini API Documentation}, 2025. [Online]. Available: \url{https://ai.google.dev/gemini-api/docs}

\bibitem{chen2024}
M.~Chen, Y.~Li, and H.~Zhang, ``Edge-cloud collaborative AI for real-time mobile anomaly detection,'' \emph{IEEE Trans. Mobile Comput.}, vol.~23, no.~5, pp.~4102--4115, 2024.

\bibitem{gupta2023}
R.~K. Gupta and P.~Sharma, ``Privacy-preserving location tracking in personal safety applications,'' \emph{Proc. ACM Secur. Privacy Workshop}, pp.~67--74, 2023.

\bibitem{park2023}
J.~Park, S.~Lee, and T.~Kim, ``Differential privacy for urban safety heatmap generation,'' \emph{IEEE Int. Conf. Data Mining (ICDM)}, pp.~312--320, 2023.

\bibitem{nij2022}
National Institute of Justice, \emph{Technology in Violence Prevention: Best Practices \& Gaps}, Washington, DC: U.S. Dept. of Justice, 2022.

\bibitem{apple2024}
Apple Inc., \emph{iOS Background Execution \& Power Management Guidelines}, 2024. [Online]. Available: \url{https://developer.apple.com/documentation/backgroundtasks}

\bibitem{ieee2023}
IEEE Std 1620-2023, \emph{Standard for Safety-Critical Mobile Application Architectures}, New York, NY: IEEE, 2023.

\bibitem{rao2024}
K.~S. Rao \emph{et~al.}, ``Hybrid rule-AI models for contextual risk assessment in IoT ecosystems,'' \emph{Sensors}, vol.~24, no.~8, Art.~2511, 2024.

\bibitem{edpb2023}
European Data Protection Board, \emph{Guidelines on Location Data \& Privacy in Mobile Applications}, Brussels, EU: EDPB, 2023.

\bibitem{firebase_functions2024}
Firebase Team, \emph{Firebase Cloud Functions \& Serverless Architecture Patterns}, Google, 2024. [Online]. Available: \url{https://firebase.google.com/docs/functions}

\bibitem{nguyen2023}
T.~A. Nguyen and L.~M. Tran, ``Battery-optimized background sensing for continuous health \& safety monitoring,'' \emph{ACM MobiCom Workshop}, pp.~45--52, 2023.

\bibitem{google_geo2024}
Google LLC, \emph{Geolocation \& Reverse Geocoding API Documentation}, 2024. [Online]. Available: \url{https://developers.google.com/maps/documentation/geolocation}

\bibitem{patel2024}
R.~S. Patel and D.~K. Singh, ``Federated learning for personalized anomaly detection in mobile safety systems,'' \emph{IEEE Access}, vol.~12, pp.~78901--78912, 2024.

\end{thebibliography}

\end{document}
