% ============================================================
% Section 8: Results & Analysis
% ============================================================
\section{Results \& Analysis}

\subsection{Evaluation Methodology}

\subsubsection{Test Environment}
Testing was conducted on Samsung Galaxy A52 (Android 13) and iPhone 13 (iOS 17) under three network conditions: Wi-Fi (stable), 4G (variable), and offline (airplane mode). A total of 30 simulated walks were performed across three categories: \textit{Low-risk} (daytime, crowded commercial area, normal walking), \textit{Medium-risk} (evening, mixed residential, occasional stops), and \textit{High-risk} (late-night 22:00--04:00, isolated route, erratic motion).

\subsubsection{Metrics Tracked}
Key evaluation metrics included: Alert Latency (target $<$3s), Detection Accuracy ($>$85\%), False Positive Rate ($<$10\%), Battery Impact ($<$15\% over 8h), and Offline Recovery Time ($<$10s).

\subsection{Quantitative Results}

Table~\ref{tab:danger_accuracy} presents danger score accuracy across test scenarios.

\begin{table}[htbp]
\caption{Danger Score Accuracy Across Scenarios (n=30)}
\label{tab:danger_accuracy}
\centering
\scriptsize
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Scenario} & \textbf{True Pos.} & \textbf{False Pos.} & \textbf{Avg Score} \\
\hline
Low-risk (n=10) & 0\% (0/10) & 7\% (1/10) & 18.3 $\pm$ 6.2 \\
\hline
Medium-risk (n=10) & 80\% (8/10) & 20\% (2/10) & 52.1 $\pm$ 11.4 \\
\hline
High-risk (n=10) & 90\% (9/10) & 0\% (0/10) & 78.6 $\pm$ 9.8 \\
\hline
\end{tabular}
\end{table}

Table~\ref{tab:performance} summarizes operational performance metrics.

\begin{table}[htbp]
\caption{Operational Performance Metrics (Avg., n=30)}
\label{tab:performance}
\centering
\scriptsize
\begin{tabular}{|l|c|c|}
\hline
\textbf{Metric} & \textbf{Result} & \textbf{Target Met} \\
\hline
Alert Latency (Wi-Fi) & 1.8 $\pm$ 0.4 s & Yes \\
\hline
Alert Latency (4G) & 2.7 $\pm$ 0.9 s & Yes \\
\hline
Offline Queue Recovery & 4.2 $\pm$ 1.1 s & Yes \\
\hline
Battery Drain (8h) & 9.3\% $\pm$ 2.1\% & Yes \\
\hline
Gemini API Latency & 1.2 $\pm$ 0.3 s & Yes \\
\hline
Rule Engine Processing & $<$ 50 ms & Yes \\
\hline
\end{tabular}
\end{table}

\subsection{Comparative Analysis: Rule-Only vs.\ Hybrid}
The hybrid (Rule+AI) approach achieved an AUC of 0.94, compared to Rule-Only (AUC = 0.87) and AI-Only (AUC = 0.91). The hybrid approach achieves the best precision-recall balance while maintaining fallback reliability during AI service disruptions.

\subsection{Qualitative User Feedback (Pilot, n=15)}
Among 15 pilot participants: 13/15 reported increased confidence walking alone at night; average System Usability Scale (SUS) score was 82.4 (``Excellent''); 2/15 expressed initial privacy hesitation, resolved after explaining data minimization; all trusted contacts correctly interpreted push notifications and location links.

\subsection{Evaluation Limitations}
The pilot study was limited to 15 users; larger deployment is needed for statistical significance. Simulated scenarios cannot fully replicate unpredictable real-world emergencies. Tests were geographically limited, and Gemini prompt performance may vary across cultural/regional contexts without fine-tuning.
